Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
addressing more comments, cite HEALPix at first mention

With $p$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ gives the residual Solar dipole
amplitude, and its best-fit value represents the scaling of the Solar dipole 
that makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly 
linear. $b$ represents the constant offset that must be subtracted from the 
band $\nu_i$ map to make its zero level consistent with that of the 857 GHz 
map. For each band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by 
performing a linear least squares fit with uniform weights and iterative 
outlier rejection. Figure \ref{fig:dip} shows scatterplots of the band $\nu_i$ 
versus 857 GHz correlation before and after correcting for the best-fit offset 
and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
are the tightened correlations striking in these scatterplots, but the residual
dipole subtractions appear very successful in the two-dimensional band $\nu_i$ 
maps themselves. Before performing thermal dust fits, we therefore subtract the
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit
offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
along with other important per-band parameters, such as the fractional 
multiplicative calibration uncertainty $c_{\nu}$.

@@

The following subsections detail our procedure for constraining the 
two-component dust emission model parameters which are permitted to vary
spatially. In the case of our full-resolution $6.1'$fits, these parameters
are the SED normalization and the hot dust temperature $T_2$. The same 
formalism will apply to our lower-resolution fits in which $f_1$ is also 
allowed to vary from one line of sight to another.

% sentence here summarizing what the following subsections will describe ?

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million 
non-overlapping pixels of angular size $\sim$1.72$'$, defined by the HEALPix 
pixelization in Galactic coordinates, with $N_{side}$=2048 \citep{healpix}. 
This pixelization is convenient because it is the same format in which the 
\PLANCK~HFI maps were released, and because it adequately samples the $6.1'$ 
FWHM maps under consideration in our full-resolution fits. Our procedure will 
fit the intensity measurements in each spatial pixel independently of those in 
neighboring pixels.

>>>>

With $p$ denoting a single nside=64 HEALPix pixel \citep{healpix} in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ gives the residual Solar dipole
amplitude, and its best-fit value represents the scaling of the Solar dipole 
that makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly 
linear. $b$ represents the constant offset that must be subtracted from the 
band $\nu_i$ map to make its zero level consistent with that of the 857 GHz 
map. For each band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by 
performing a linear least squares fit with uniform weights and iterative 
outlier rejection. Figure \ref{fig:dip} shows scatterplots of the band $\nu_i$ 
versus 857 GHz correlation before and after correcting for the best-fit offset 
and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
are the tightened correlations striking in these scatterplots, but the residual
dipole subtractions appear very successful in the two-dimensional band $\nu_i$ 
maps themselves. Before performing thermal dust fits, we therefore subtract the
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit
offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
along with other important per-band parameters, such as the fractional 
multiplicative calibration uncertainty $c_{\nu}$.

@@

The following subsections detail our procedure for constraining the 
two-component dust emission model parameters which are permitted to vary
spatially. In the case of our full-resolution $6.1'$ fits, these parameters
are the SED normalization and the hot dust temperature $T_2$. The same 
formalism will apply to our lower-resolution fits in which $f_1$ is also 
allowed to vary from one line of sight to another.

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
is the same format in which the \PLANCK~HFI maps were released, and because it 
adequately samples the $6.1'$ FWHM maps under consideration in our 
full-resolution fits. Our procedure will fit the intensity measurements in each
spatial pixel independently of those in neighboring pixels.
